Supplementary Information: \nTree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2020-07-13 manuscript/climate_sensitivity_SI.Rmd
add draft S5

\newpage
![Figure S4: Comparison of Rt and ARIMA results, with residuals, for each drought scenario](tables_figures/publication/figureS4_Rt_arima_comparison.png)

>>>>

\newpage
![Figure S4: Comparison of $Rt$ and $Rt_{ARIMA}$ results, with residuals, for each drought scenario](tables_figures/publication/figureS4_Rt_arima_comparison.png)

\newpage
![Figure S5: **PLACEHOLDER** ](tables_figures/publication/figureS5_species Rt differences.png)
